The persuasion of symbolic elements in government public communications, and their moderation by personal relevance

### 2019-07-16 paper3_relevance and symbols_revision_01.Rmd
Add files via upload

```{r silent-packages, echo = FALSE, eval = TRUE, message=FALSE, include = FALSE}
library(knitr)
library(tidyverse)
library(stargazer)
library(car)
library(broom)
library(kableExtra)
library(ggthemes)
library(lmtest)
library(sandwich)
library(ggpubr)
library(effsize)
library(emmeans)
```

```{r,echo=FALSE,warning=FALSE,message=FALSE}
N_raw = nrow(SVIVA2_raw_00)
N_0=SVIVA2_00%>%nrow()
N_1=SVIVA2_01%>%nrow()

@@

```{r, echo=FALSE, warning=FALSE, message=F}
#Figures and tables
table.x=0
figure.x=0
```

@@

EPM is a national-level bureau responsible for the formulation, coordination, and execution of environmental policy in Israel. Among others, EPM is responsible for monitoring and regulating the air quality across the country. The Haifa-Bay area, located in the north of Israel, has been characterized by relatively high levels of air pollution, mainly due to the Haifa-Bay industrial zone, which is located in proximity of a number of urban residential areas. It is considered the largest industrial zone in the country, with concentration of multiple oil refineries, power plants, and chemical factories. Beginning in Mid 2000s, EPM has been developing and implementing a series of policy programs to monitor and reduce the high levels of pollution specifically in that area [@theministryofenvironmentprotection_2015; @theministryofenvironmentprotection_2015a; @theministryofenvironmentprotection_2019]. While EPM has claimed that its programs have been effective and led to a significant reduction in air-pollution levels, local residents, professionals and other public agencies have remained highly concerned about the issue, and  accordingly it remained high on the public agenda [@statecomptrollerofisrael_2019]. Specifically, the issue received much media and public attention in 2015-2016, following a series of reportings an media publications about the health consequences of the air-pollution in Haifa-Bay. In 2015, the Ministry of Health published statistical data indicating that Haifa-Bay residents experience significantly higher rates of cancer and asthma, compared to other areas of the country. The subsequent media reports specifically highlighted the conclusion that half of the cases of cancer among children in the area can be associated to air-pollution [@elroi_website_2015; @raavad_website_2015]. Thereafter, in 2016, media reporters revealed the interim results of a large epidemiological study, establishing a link between air-pollution in the Haifa-Bay and certain types of cancer, as well as abnormal measurements of newborn babies and growth curves of infants.[^footnote_epidemiological_study] The media reports of that study repeatedly focused on the finding that babies in the Haifa-Bay are born with "smaller heads" [@koriel_website_2016; @rinat_website_2016; @rivlin_website_2016]. Some reports also highlighted that the areas that are geographically closer to the industrial areas are found to be at higher risk for cancer [@bendavid_website_2016]. These publications, and others, caused much panic among the local population, and especially among young parents.

@@

```{r, echo=FALSE, warning=FALSE, message=F}
alpha_air_trust = psych::alpha(select(SVIVA2_01, TRUST_air_q1,
                               TRUST_air_q2,
                               TRUST_air_q3,
                               TRUST_air_q4,
                               TRUST_air_q5,
                               TRUST_air_q6))[["total"]][["raw_alpha"]]%>%round(2)

@@

Living in Haifa-bay area was coded according to respondents’ reporting of residence, work or studying in one of the Haifa-Bay cities. To confirm the empirical assumption that the air-pollution policy (but not the recycling policy) is perceived as more personally relevant by Haifa Bay residents compared with center residents, respondents were asked, after the outcome variable items: "To what extent did you feel that the policy on ["Reducing the air-pollution in the Haifa-Bay" / “reducing waste and increasing recycling”] is personally relevant to you?" (1="very little"; 7="very much"). `r figure.x=figure.x+1`**Figure `r figure.x`** shows the distributions of the latter items across the two areas. As expected, the air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents  (Cohen's D = `r relevance.areas.d[["estimate"]] %>% round(2)` [`r relevance.areas.d[["conf.int"]][["lower"]] %>% round(2)`,`r relevance.areas.d[["conf.int"]][["upper"]] %>% round(2)`]). By comparison, the recycling policy is perceived by both groups as relatively personally relevant by both groups, with no statistically significant differences between them. Additional support for these differences are provided by respondents' answers to the open question about the most salient environmental issue in their area of residence, which was presented to the relevance treatment group (i.e. before presenting the policy plans). Indeed, `r t1<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow()``r t1` of the `r t2<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1) %>% nrow()``r t2` Haifa-Bay subjects who were asked this question regarded in their responses to the air-pollution generated from the industrial area (`r (t1/t2*100) %>% round(0)`%).[^footnote_air_relevance_coding] Moreover, many Haifa-Bay respondents explicitly linked the air-pollution to higher morbidity rates in their area. Subjects from center cities regarded to a variety of issues, including recycling, traffic jams and cleanliness, and only `r ((SVIVA2_01_center %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow())/nrow(SVIVA2_01_center)*100) %>% round(0)`% of them mentioned air-pollution as a prominent environmental concern in their area.

[^footnote_air_relevance_coding]: I coded any reference to either air-pollution or the chemical factories in the Haifa-Bay area, as related to air-pollution.

@@

```{r, echo=FALSE, warning=FALSE, message=F}
mod_air_null = lm(TRUST_air_INDEX~1,data=SVIVA2_01_comb)

@@

```{r, echo=FALSE, warning=FALSE, message=F}

@@

SVIVA2_01_comb.haifa <- SVIVA2_01_comb.haifa %>% 
  mutate(RELEVANCE_exp.r = Recode(RELEVANCE_exp,"0=1;1=0"))

@@

@@

@@

Two limitations about these analyses should be acknowledged. First, since the treatment manipulation did not affect participants' self-reporting of the personal relevance, there is no certainty that the manipulation actually succeeded in priming those subjects. Second, these analyses have more limited statistical power, compared to the observational comparisons, since they are restricted only to the sample of Haifa-Bay subjects. Still, even if the relevance manipulation does attenuate the effect of the real symbols, their effect on that group compared with the no symbols is estimated based on Model `r table.x`.2 as `r (diff5/sd.air.haifa) %>% round(3)` SDs (lower 95% CI = `r ((diff5 - 1.96*se5)/sd.air.haifa) %>% round(3)`--`r ((diff5 + 1.96*se5)/sd.air.haifa) %>% round(3)`). This indicates that even Haifa-Bay residents that were reminded in a subtle way about the relevance of the air-pollution to their lives area are affected, at least to some degree, by familiar symbols. As for the information manipulation, descriptively, only `r ((filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==1,INFORMATION_weak==1,TRUST_air_INDEX<=2) %>% nrow())/(nrow(filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==0,INFORMATION_weak==1)))*100)%>% round(0)`% of the participants assigned to relevance treatment reported a low score of 2 or less for the weak policy plan, while `r ((filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==1,INFORMATION_weak==1,TRUST_air_INDEX>=4) %>% nrow())/(nrow(filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==1,INFORMATION_weak==1)))*100)%>% round(0)`% of them reported a trust score of 4 or more (percentages for the control group are `r ((filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==0,INFORMATION_weak==1,TRUST_air_INDEX<=2) %>% nrow())/(nrow(filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==0,INFORMATION_weak==1)))*100)%>% round(0)`% and `r ((filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==0,INFORMATION_weak==1,TRUST_air_INDEX>=4) %>% nrow())/(nrow(filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==0,INFORMATION_weak==1)))*100)%>% round(0)`%, respectively). This entials that a vast majority of subjects within the polluted area tended to trust, to some degree, a policy plan whose chances of reducing the air-pollution are extremely low, even after reminding them about the relevance of the issue.

```{r, echo=FALSE, warning=FALSE, message=F}
mod_closedness_null = lm(TRUST_air_INDEX~+
                   GOV_TRUST+
                   IDEOLOGY+
                   EDUCATION+
                   INCOME+
                     AGE,data=SVIVA2_01_comb.haifa)

@@

library(effsize)

@@

**Haifa-Bay**
```{r, echo=FALSE, warning=FALSE, message=F}

@@

<br>
**Center**
```{r, echo=FALSE, warning=FALSE, message=F}

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=8,fig.height=4}
SVIVA2_01 %>%
  select(AREA_names,
         RELEVANCE_air_obs,
         RELEVANCE_waste_obs) %>% 
  gather(key = policy, value = relevance, -AREA_names) %>%
  mutate(policy = Recode(policy,"'RELEVANCE_air_obs'='Air-pollution policy';'RELEVANCE_waste_obs'='Recycling policy'")) %>% 
ggplot(aes(AREA_names,relevance))+ 
  theme_tufte()+
  geom_boxplot(width=0.25,color="gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               fun.args = list(mult = 1.96),
               width=0.05,size=0.5) + 
  stat_summary(fun.y = mean, geom = "point", size=1.6)+
  facet_grid(~policy)+
  xlab("")+
  scale_y_continuous(name = "Perceived personal relevance",limits=c(1,7),breaks = seq(1,7,by=1))
```
<font size="0.5">

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=8,fig.height=4}
p1 <- SVIVA2_01_comb %>%
ggplot(aes(SYMBOL_n,TRUST_air_INDEX))+ 
  theme_tufte()+
  geom_boxplot(width=0.25,color="gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               fun.args = list(mult = 1.96),
               width=0.05,size=0.5) + 
  stat_summary(fun.y = mean, geom = "point", size=1.6)+
  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = 1))+
  scale_x_discrete(name = "",labels = c("No symbols","Fake symbols","Real symbols"))+
  scale_y_continuous(name = "Trust in air-pollution policy",limits=c(1,7),breaks = seq(1,7,by=1))+
  ggtitle("Symbols")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.width=8}
p1 <- SVIVA2_01_comb %>%
  filter(policy=="TRUST_air_INDEX") %>% 
ggplot(aes(factor(SYMBOL_n),trust,shape=factor(AREA_names)))+ 
  theme_tufte()+
  #geom_boxplot(width=0.25,color="gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               fun.args = list(mult = 1.96),
               width=0.1,size=0.5,position=position_dodge(0.1),color="gray70") + 
  stat_summary(fun.y = mean, geom = "point", size=1.6,position=position_dodge(0.1))+
  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = AREA_names,linetype=AREA_names),position=position_dodge(0.1),alpha=0.8)+
  scale_shape_manual(guide=F, values=c(19,1))+
  scale_linetype_manual(guide=F, values=c(1,4))+
  scale_x_discrete(name="",labels=c("No symbols","Fake symbols","Real symbols"))+
  scale_y_continuous(name = "Trust in air-pollution policy",breaks = seq(1,7,by=0.5))+
  ggtitle("Symbols")

@@

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
control.vars <- c("GENDER",
                  "AGE",
                  "GOV_TRUST",
                   "IDEOLOGY",
                   "EDUCATION",
                   "INCOME",
                   "CHILDREN",
                   "CHILDREN_young")

@@

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
control.vars <- c("GENDER",
                  "AGE",
                  "GOV_TRUST",
                   "IDEOLOGY",
                   "EDUCATION",
                   "INCOME",
                   "CHILDREN_young")

@@

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
control.vars <- c("GENDER",
                  "AGE",
                  "GOV_TRUST",
                   "IDEOLOGY",
                   "EDUCATION",
                   "INCOME")

>>>>

```{r silent-packages}
library(knitr)
library(tidyverse)
library(stargazer)
library(car)
library(broom)
library(kableExtra)
library(ggthemes)
library(lmtest)
library(sandwich)
library(ggpubr)
library(effsize)
library(emmeans)
```

```{r}
N_raw = nrow(SVIVA2_raw_00)
N_0=SVIVA2_00%>%nrow()
N_1=SVIVA2_01%>%nrow()

@@

```{r}
#Figures and tables
table.x=0
figure.x=0
```

@@

EPM is a national-level bureau responsible for the formulation, coordination, and execution of environmental policy in Israel. Among others, EPM is responsible for monitoring and regulating the air quality across the country. The Haifa-Bay area, located in the north of Israel, has been characterized by relatively high levels of air pollution, mainly due to the Haifa-Bay industrial zone, which is located in proximity of a number of urban residential areas. It is considered the largest industrial zone in the country, with concentration of petrochemical industries, including oil refineries, power plants, and chemical factories. Beginning in Mid 2000s, EPM has been developing and implementing a series of policy programs to monitor and reduce the high levels of pollution specifically in that area [@theministryofenvironmentprotection_2015; @theministryofenvironmentprotection_2015a; @theministryofenvironmentprotection_2019]. While EPM has claimed that its programs have been effective and led to a significant reduction in air-pollution levels, local residents, professionals and other public agencies have remained highly concerned about the issue, and  accordingly it remained high on the public agenda [@statecomptrollerofisrael_2019]. Specifically, the issue received much media and public attention in 2015-2016, following a series of reportings an media publications about the health consequences of the air-pollution in Haifa-Bay. In 2015, the Ministry of Health published statistical data indicating that Haifa-Bay residents experience significantly higher rates of cancer and asthma, compared to other areas of the country. The subsequent media reports specifically highlighted the conclusion that half of the cases of cancer among children in the area can be associated to air-pollution [@elroi_website_2015; @raavad_website_2015]. Thereafter, in 2016, media reporters revealed the interim results of a large epidemiological study, establishing a link between air-pollution in the Haifa-Bay and certain types of cancer, as well as abnormal measurements of newborn babies and growth curves of infants.[^footnote_epidemiological_study] The media reports of that study repeatedly focused on the finding that babies in the Haifa-Bay are born with "smaller heads" [@koriel_website_2016; @rinat_website_2016; @rivlin_website_2016]. Some reports also highlighted that the areas that are geographically closer to the industrial areas are found to be at higher risk for cancer [@bendavid_website_2016]. These publications, and others, caused much panic among the local population, and especially among young parents.

@@

```{r}
alpha_air_trust = psych::alpha(select(SVIVA2_01, TRUST_air_q1,
                               TRUST_air_q2,
                               TRUST_air_q3,
                               TRUST_air_q4,
                               TRUST_air_q5,
                               TRUST_air_q6))[["total"]][["raw_alpha"]]%>%round(2)

@@

Living in Haifa-bay area was coded according to respondents’ reporting of residence, work or studying in one of the Haifa-Bay cities. To confirm the empirical assumption that the air-pollution policy (but not the recycling policy) is perceived as more personally relevant by Haifa Bay residents compared with center residents, respondents were asked, after the outcome variable items: "To what extent did you feel that the policy on ["Reducing the air-pollution in the Haifa-Bay" / “reducing waste and increasing recycling”] is personally relevant to you?" (1="very little"; 7="very much"). `r figure.x=figure.x+1`**Figure `r figure.x`** shows the distributions of the latter items across the two areas. As expected, the air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents  (Cohen's D = `r relevance.areas.d[["estimate"]] %>% round(2)` [`r relevance.areas.d[["conf.int"]][["lower"]] %>% round(2)`,`r relevance.areas.d[["conf.int"]][["upper"]] %>% round(2)`]). By comparison, the recycling policy is perceived by both groups as relatively personally relevant by both groups, with no statistically significant differences between them. Additional support for these differences are provided by respondents' answers to the open question about the most salient environmental issue in their area of residence, which was presented to the relevance treatment group (i.e. before presenting the policy plans). Indeed, `r t1<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow()``r t1` of the `r t2<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1) %>% nrow()``r t2` Haifa-Bay subjects who were asked this question regarded in their responses to the air-pollution generated from the industrial area (`r air.content.percent.haifa <- t1/t2*100``r air.content.percent.haifa %>% round(0)`%).[^footnote_air_relevance_coding] Moreover, many Haifa-Bay respondents explicitly linked the air-pollution to higher morbidity rates in their area. Subjects from center cities regarded to a variety of issues, including recycling, traffic jams and cleanliness, and only `r ((SVIVA2_01_center %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow())/nrow(SVIVA2_01_center)*100) %>% round(0)`% of them mentioned air-pollution as a prominent environmental concern in their area.

```{r}
library(irr)

df.air.content.reliability <- relevance.coding[1:231,] %>% 
  select(air.content,
         air.content.coder2) %>% 
  drop_na(air.content.coder2) %>% 
  as.matrix() %>% 
  t()

[^footnote_air_relevance_coding]: I coded any reference to either air-pollution or the chemical factories in the Haifa-Bay area, as related to air-pollution. To confirm inter-coder reliability, a second coder independently coded 70 observations (Krippendorff’s alpha = `r kripp.alpha(df.air.content.reliability)[["value"]] %>% round(2)`).

@@

```{r}
mod_air_null = lm(TRUST_air_INDEX~1,data=SVIVA2_01_comb)

@@

```{r}

@@

SVIVA2_01_comb.haifa <- SVIVA2_01_comb.haifa %>% 
  mutate(RELEVANCE_exp.r = Recode(RELEVANCE_exp,"0=1;1=0"),
         SYMBOL_t.r = Recode(SYMBOL_t,"0=2;2=0"))

@@

mod_relevance_1.2.r.r = update(mod_relevance_null,. ~ .+RELEVANCE_exp.r*(SYMBOL_t.r+INFORMATION_weak))

@@

mod_symbols_relevance_aircontent = lm(TRUST_air_INDEX ~ SYMBOL_t,SVIVA2_01_haifa.relevance.aircontent)

mod_symbols_relevance_aircontent.r = lm(TRUST_air_INDEX ~ SYMBOL_t.r,SVIVA2_01_haifa.relevance.aircontent)

main.symbols.relevance.aircontent <- emmeans::emmeans(mod_symbols_relevance_aircontent, specs = pairwise ~ SYMBOL_t)

t.symbols.relevance.aircontent.no <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_haifa.relevance.aircontent %>% filter(SYMBOL_t!=2))
t.symbols.relevance.aircontent.fake <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_haifa.relevance.aircontent %>% filter(SYMBOL_t!=0))

@@

Two limitations about these analyses should be acknowledged. First, since the treatment manipulation did not affect participants' self-reporting of the personal relevance, there is no certainty that the manipulation actually succeeded in priming those subjects. Second, these analyses have more limited statistical power, compared to the observational comparisons, since they are restricted only to the sample of Haifa-Bay subjects. Still, even if the relevance manipulation does attenuate the effect of the real symbols, their effect on that group compared with the no symbols is estimated based on Model `r table.x`.2 as `r (diff5/sd.air.haifa) %>% round(3)` SDs [`r ((diff5 - 1.96*se5)/sd.air.haifa) %>% round(3)`,`r ((diff5 + 1.96*se5)/sd.air.haifa) %>% round(3)`]. Remarkably, even when restricting the relevance treatment group to those who mentioned the air-pollution as an acute environmental issue in their area of residence (`r air.content.percent.haifa %>% round(0)`% of that group, *n* = `r SVIVA2_01_haifa.relevance.aircontent %>% nrow()`), the real symbols still had a roughly similar positive effect on trust in the policy plan, compared with the no symbols (*diff* = `r (main.symbols.relevance.aircontent$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.relevance.aircontent.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.relevance.aircontent.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.relevance.aircontent.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).[^footnote_relevance_significance_fakesymbols] This indicates that even Haifa-Bay residents that were reminded about the relevance of the air-pollution to their lives area are positively affected, at least to some degree, by familiar symbols.

[^footnote_relevance_significance_fakesymbols]: Consistently with the previous models, subjects in the real symbols group also reported higher trust compared with the fake symbols, but these differences are not sufficiently significant. The differences between the two control groups are insignificant.

```{r}
mod_closedness_null = lm(TRUST_air_INDEX~+
                   GOV_TRUST+
                   IDEOLOGY+
                   EDUCATION+
                   INCOME+
                     AGE,data=SVIVA2_01_comb.haifa)

@@

@@

**Haifa-Bay**
```{r}

@@

<br>
**Center**
```{r}

@@

```{r, fig.width=8,fig.height=4}
SVIVA2_01 %>%
  select(AREA_names,
         RELEVANCE_air_obs,
         RELEVANCE_waste_obs) %>% 
  gather(key = policy, value = relevance, -AREA_names) %>%
  mutate(policy = Recode(policy,"'RELEVANCE_air_obs'='Air-pollution policy';'RELEVANCE_waste_obs'='Recycling policy'")) %>% 
ggplot(aes(AREA_names,relevance))+ 
  theme_tufte()+
  geom_boxplot(width=0.25,color="gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               fun.args = list(mult = 1.96),
               width=0.05,size=0.5) + 
  stat_summary(fun.y = mean, geom = "point", size=1.6)+
  facet_grid(~policy)+
  xlab("")+
  scale_y_continuous(name = "Perceived personal relevance",limits=c(1,7),breaks = seq(1,7,by=1))
```
<font size="0.5">

@@

```{r, fig.width=8, fig.height=4}
p1 <- SVIVA2_01_comb %>%
ggplot(aes(SYMBOL_n,TRUST_air_INDEX))+ 
  theme_tufte()+
  geom_boxplot(width=0.25,color="gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               fun.args = list(mult = 1.96),
               width=0.05,size=0.5) + 
  stat_summary(fun.y = mean, geom = "point", size=1.6)+
  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = 1))+
  scale_x_discrete(name = "",labels = c("No symbols","Fake symbols","Real symbols"))+
  scale_y_continuous(name = "Trust in air-pollution policy",limits=c(1,7),breaks = seq(1,7,by=1))+
  ggtitle("Symbols")

@@

```{r, fig.width=8}
p1 <- SVIVA2_01_comb %>%
  filter(policy=="TRUST_air_INDEX") %>% 
ggplot(aes(factor(SYMBOL_n),trust,shape=factor(AREA_names)))+ 
  theme_tufte()+
  #geom_boxplot(width=0.25,color="gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               fun.args = list(mult = 1.96),
               width=0.1,size=0.5,position=position_dodge(0.1),color="gray70") + 
  stat_summary(fun.y = mean, geom = "point", size=1.6,position=position_dodge(0.1))+
  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = AREA_names,linetype=AREA_names),position=position_dodge(0.1),alpha=0.8)+
  scale_shape_manual(guide=F, values=c(19,1))+
  scale_linetype_manual(guide=F, values=c(1,4))+
  scale_x_discrete(name="",labels=c("No symbols","Fake symbols","Real symbols"))+
  scale_y_continuous(name = "Trust in air-pollution policy",breaks = seq(1,7,by=0.5))+
  ggtitle("Symbols")

@@

```{r,results="asis"}
control.vars <- c("GENDER",
                  "AGE",
                  "GOV_TRUST",
                   "IDEOLOGY",
                   "EDUCATION",
                   "INCOME",
                   "CHILDREN",
                   "CHILDREN_young")

@@

```{r,results="asis"}
control.vars <- c("GENDER",
                  "AGE",
                  "GOV_TRUST",
                   "IDEOLOGY",
                   "EDUCATION",
                   "INCOME",
                   "CHILDREN_young")

@@

```{r,results="asis"}
control.vars <- c("GENDER",
                  "AGE",
                  "GOV_TRUST",
                   "IDEOLOGY",
                   "EDUCATION",
                   "INCOME")
